Estimating the magnetization distribution within rectangular rock samples

### 2016-06-18 manuscript/manuscript.tex
rerun the sensor-to-sample distance test for including the averaging effect produced by the finite active area of the magnetic sensor and also the random position noise in the distance h of observation points located on each acquisition line. The changes also include text adaptations.

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the simulated magnetic sensor has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}). Besides,
the magnetic data produced by the synthetic sample on 
each plane $\alpha$, $\alpha = 0, 1, 2, 3$, were calculated on
a regular grid of $102 \times 42$ points along the $x$ and 
$y$/$z$ axes, respectively, and were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30,000$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

Unlike the previous tests, the simulated noise-corrupted 
data used here were calculated at a different distance $h$ 
(Figure \ref{fig:sample-planes-cross}) between each observation
plane and the surface of the sample.
The distances $h$ between the sample surface and the planes 
$\alpha = 0, 1, 2$ and $3$ are equal to $420$~$\mu$m, $330$~$\mu$m,
$400$~$\mu$m and $230$~$\mu$m, respectively.
The noise-corrupted magnetic data were properly corrected 
from the misalignment problems by using the parameters shown in 
Table \ref{tab:misalignment-parameters} and the equations 
\ref{eq:pre-processing} and \ref{eq:pre-processing-R}.
As in the previous tests, we applied our method by using
an interpretation model with side lengths $L_{x}$, $L_{y}$ 
and $L_{z}$ equal to the true ones and with the same number 
of prisms ($P = 16$) as the synthetic sample along the $x$-axis.
We have applied our method to invert the noise-corrupted magnetic 
data without, however, consider the variations in the 
sensor-to-sample distances $h$. Instead, we presumed a constant
distance $h = 500$~$\mu$m between all the planes and the surface
of the sample.

>>>>

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the simulated magnetic sensor has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}). Besides,
the magnetic data produced by the synthetic sample on 
each plane $\alpha = 0, 1, 2, 3$ were calculated at
$N = 4,284$ points, on a set of $42$ regularly spaced lines 
that are parallel to the $x$-axis, each one with $102$ regularly
spaced points. The data were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30,000$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

Unlike the previous tests, the distance $h$ 
(Figure \ref{fig:sample-planes-cross}) between the 
surface of the sample and the observation
points at each plane is not constant.
Let us first remember that, on each plane $\alpha = 0, 1, 2, 3$,
the observation points are located on a set 
of $42$ regularly-spaced acquisition 
lines, each one with $102$ regularly spaced points.
In this test, the distance $h$ is contaminated with a
Gaussian position noise having a common standard deviation of
$100$~$\mu$m and a different mean value equal to 
$420$~$\mu$m, $330$~$\mu$m, $400$~$\mu$m and $230$~$\mu$m
on each plane $\alpha = 0, 1, 2, 3$, respectively.
The distance $h$, however, is constant for observation points 
located on the same acquisition line.

The noise-corrupted magnetic data were properly corrected 
from the misalignment problems by using the parameters shown in 
Table \ref{tab:misalignment-parameters} and the equations 
\ref{eq:pre-processing} and \ref{eq:pre-processing-R}.
As in the previous tests, we applied our method by using
an interpretation model with side lengths $L_{x}$, $L_{y}$ 
and $L_{z}$ equal to the true ones and with the same number 
of prisms ($P = 16$) as the synthetic sample along the $x$-axis.
We have applied our method to invert the noise-corrupted magnetic 
data without, however, consider the variations in the 
sensor-to-sample distances $h$. Instead, we presumed a constant
distance $h = 500$~$\mu$m between all the planes and the surface
of the sample.
